Impact of Demographics and Skills of the Observer on Visual Statistical Inference

### 2013-05-23 sociology_paper.tex
Age and study figures added

>>>>

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=3.5in]{country_study_bar.pdf} 
   \caption{Countrywise distribution of education level of the MTurk workers participating the experiments. The spike in graduate degree in India may be due to their consideration of undergraduate degree to be graduate degree as well.}
   \label{fig:country_study}
\end{figure}

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=3.5in]{age_study_bar.pdf} 
   \caption{Countrywise distribution of age levels of the MTurk workers participating the experiments.}
   \label{fig:age_study}
\end{figure}
